%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Original author:
% Rahul Chauhan (http://rahulchauhan.net)
%
% Original repository:
% https://github.com/rahulworld/rahulworld-Resume
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{rahulworld-resume}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 
\begin{Huge}
	\headername{Alok Gaur}\\
\end{Huge}
\begin{LARGE}
	\textbf{\\DevOps Engineer}
\end{LARGE}
\hspace*{0pt}\hfill    \\
\hspace*{0pt}\hfill    \\
\hspace*{0pt}\hfill    \\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     summary
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section[14pt]{Summary} 
\noindent\rule{5cm}{0.4pt}
\begin{large}
Hands-on experience in cloud architecture, automating and optimizing mission critical deployments over large infrastructure.\\
Proficient in Linux with AWS Cloud, Docker and in developing CI/CD pipeline.
\end{large}

\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Skills}
\noindent\rule{5cm}{0.4pt}
\subsection{OS}
GNU/Linux, Windows
\vspace{6pt}

\vspace{6pt}
\subsection{Linux}
User Management, cron job SSH, LVMs, \\ Selinux, Firewall, NFS/Autofs, ISCSI, SAMBA, \\Logs, HTTP Configuration

\vspace{6pt}
\subsection{Ansible}
AdHoc, Playbook, Security, Facts, Roles

\vspace{6pt}
\subsection{AWS}
EC2, VPC, S3, Elastic BeanStalk, Cloudfront, \\Cloudformation, R53, IAM

\vspace{6pt}
\subsection{Docker}
Dockerfile, Docker Compose, Volume, Docker Swarm

\vspace{6pt}
\subsection{Jenkins}
Master Slave Configuration, \\Plugins, Job build, CI/CD, Pipeline
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Education} 
\noindent\rule{5cm}{0.4pt}\\
\datecolor{June 2019}
\subsection{B.Tech. in CSE}
Kalinga University, Atal Nagar (C.G.) \\
Percentage : 87.4\\
\vspace{8pt}
\datecolor{March, 2015}
\subsection{Intermediate}
Maharishi Vidya MAndir-I,Raipur(C.G.)\\
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Interests}
\noindent\rule{5cm}{0.4pt}

Cloud Migration\\
DevOps Tools\\
Finetech\\

\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.62\textwidth} 
% \descript{BS in Computer ence}
\hspace*{0pt}\hfill    \\
\hspace*{0pt}\hfill    \\
\hspace*{0pt}\hfill Raipur, Chhattisgarh -493111, India \\
\hspace*{0pt}\hfill Mob.: +91-8449368522 / 7000604645\\
\hspace*{0pt}\hfill Email.:\textbf{\href{mailto:gauralok1710@gmail.com}{gauralok1710@gmail.com}} \\
\hspace*{0pt}\hfill Github:// \href{https://github.com/gauralok1710}{\custombold{gauralok1710}} \\
\hspace*{0pt}\hfill LinkedIn://  \href{https://www.linkedin.com/in/gauralok1710}{\custombold{gauralok1710}} \\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experience}
\noindent\rule{12.5cm}{0.4pt}
\datecolor{03/2021 - 06/2021} \runsubsection{MIST, Raipur}
\descript{Corporate Tainer }
\noindent
\hspace{2em}%
\begin{minipage}{0.95\textwidth\vspace{4pt}}
Trained students in RHCSA and AWS and guided them for certification programmes.
Created and provided live examples related to the content, in the process of  creating LVMs, Selinux, Firewall with apache configuration. And deployed web-apps using R-53, configured Elastic beanstalks, created cloud server using cloud formation and Cloudfront CDN with S3 storage. Also creating a CI/CD pipeline using Jenkins for the project available in repository in Github.
\end{minipage}
\sectionsep

\datecolor{03/2019 - 03/2021} \runsubsection{AKF IMPEX, Durg}
\descript{Asst ERP Cordinator }
\noindent
\hspace{2em}%
\begin{minipage}{0.95\textwidth\vspace{2pt}}
Automated many functions related to technology, services, and human resources, thus freeing up company manpower and providing support related to this function.
Developed and integrated the company's relevant ideas, and assisted in resource-planning decisions.
Provided support for FarmERP systems for my company which has significant online presence.
\end{minipage}
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Certificate
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Certification / Training} 
\noindent\rule{12.5cm}{0.4pt}
\datecolor{25/05/2021} \runsubsection{AWS Solution Architect}
\descript{Certified}
\noindent
\hspace{5em}%

\datecolor{2020-now } \runsubsection{Grras Pvt Ltd, Jaipur}
\descript{}
\noindent
\hspace{2em}%
\begin{minipage}{0.95\textwidth\vspace{2pt}}
In this Institute I have pursued LINUX, ANSIBLE, AWS, DOCKER and JENKINS
\end{minipage}
\datecolor{2018        } \runsubsection{3G Solution, Raipur}
\descript{}
\noindent
\hspace{2em}%
\begin{minipage}{0.95\textwidth\vspace{2pt}}
In this IT company I did training in HTML, CSS and JavaScript
\end{minipage}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SIDE PROJECT
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Side Project}
\noindent\rule{12.5cm}{0.4pt}
\datecolor{2019} \runsubsection{AI BOT}
\descript{JavaScript}
\noindent
\hspace{2em}%
\begin{minipage}{0.95\textwidth\vspace{5pt}}
Made a bot that plays a modified version of Ultimate Tic-Tac-Toe using
minimax algorithm and alpha-beta pruning.
\end{minipage}
\datecolor{2018} \runsubsection{Small Project}
\descript{PHP, JavaScript, JQuery and CodeIgnitor}
\noindent
\hspace{2em}%
\begin{minipage}{0.95\textwidth\vspace{5pt}}
Built a Dynamic Website for a Mega Spray organization.
\end{minipage}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Achievements/Awards} 
\noindent\rule{12.5cm}{0.4pt}
\datecolor{08/04/2018} \runsubsection{9th IYSC}
\descript{Participant}
\noindent
\hspace{2em}%
\begin{minipage}{0.95\textwidth\vspace{2pt}}
Presented paper titled "Frightening Truth About Indian Food Waste" at " 9th INDIAN YOUTH SCIENCE CONGRESS" in Hamirpur.
\end{minipage}
\datecolor{04/12/2018} \runsubsection{NCRIC-2018, Atal Nagar}
\descript{Participant}
\noindent
\hspace{2em}%
\begin{minipage}{0.95\textwidth\vspace{2pt}}
Participated in National Conference on "Recent Innovation in Smart IT $&$ Communication for Rural Development" at Kalinga University.
\end{minipage}
\datecolor{2018     } \runsubsection{Academic Performance}
\descript{Gold Medal}
\noindent
\hspace{2em}%
\begin{minipage}{0.95\textwidth\vspace{2pt}}
Won two gold medal in academic in my college.
\end{minipage}

\end{minipage} 
\end{document}  \documentclass[]{article}
